\documentclass{exam}

\pagenumbering{gobble}
\usepackage{titling}
\setlength{\droptitle}{-8ex}
\pretitle{\begin{flushleft}\Large\bfseries}
\posttitle{\par\end{flushleft}}
\preauthor{\begin{flushleft}\Large}
\postauthor{\end{flushleft}}
\predate{\begin{flushleft}}
\postdate{\end{flushleft}}
\usepackage{enumerate} %for alphabetized lists
\usepackage{amsmath}
\usepackage{multicol} %for multiple columns
\usepackage{systeme} %systems of equations
\renewcommand{\questionshook}{\setlength{\itemsep}{15pt}} %controls space betweenites

%fromhttps://texblog.org/2012/06/25/adding--lines--for--taking--handwritten--notes--in--latex/
\usepackage{pgffor, ifthen}
\newcommand{\notes}[3][\empty]{%q
   vspace{10pt}\\
    \foreach \n in {1,...,#2}{%
        \ifthenelse{\equal{#1}{\empty}}
            {\rule{#3}{0.5pt}\\}
            {\rule{#3}{0.5pt}\vspace{#1}\\} 
        }
}

\title{Problem set: Using the adjugate and determinant of a matrix to solve real world problems  }

\author{ \textbf{Name: }  \enspace\hrulefill \\ Precalculus \\ Herbert H. Lehman High School } 


\begin{document}
\maketitle
\thispagestyle{empty}

\noindent\textbf{Be sure to...} Do all work in your notebook.  If you don't complete work in class, finish at home. Submit on Google Classroom.
\begin{questions}
\question 
For the matrices below, \textbf{be sure to} (i) find the determinant and adjugate for each, then (ii) use these to find the inverse of the matrix (if possible). If an inverse can't be found, explain why not:

\begin{parts}
\part
$
A = \begin{bmatrix}
6  & -7 \\
-3 &  4
\end{bmatrix}
$
\part

$
A = \begin{bmatrix}
6  & 12 \\
2 &  4
\end{bmatrix}
$

\end{parts}

\question
For the system of linear equations below, \textbf{be sure to}:
\begin{multicols}{2}
\begin{enumerate}[i.]
\item Convert into a matrix equation $AX=B$
\item Find the determinant and adjugate for A 
\item Find the inverse of A
\item Use the inverse of A to solve the system of equations
\end{enumerate}
\columnbreak

$
\systeme{
5x + 4y =  3,
2x + 2y = 4
}
$
\end{multicols}

\question
Dr. Galvez and Dr. Guillermo are testing a new  experimental medicine (Precalodine) at Montefiore Hosptial.  The medicine is being given to a total of 100 patients.  Patients take the medicine in a 1 liter solution, meaning that some percent of the solution is the medicine, and the rest is water.  If patients are being given 2\% or 4\% solutions, and 2.5 liters of the medicine are on hand, how many patients will be given the 2\% solution and how many should be given the 4\%, with all the medicine used up?

\textbf{Be sure to:}
\begin{parts}
\part Create a system of linear equations corresponding to this problem
\part Rewrite your system of equations as $AX=B$
\part Use your knowledge of matrix adjugate and determinant to figure out how many patients can be given the 4\% solution.

\end{parts}

\question \textbf{Challenge!!!!} Now Dr. Galvez and Dr. Guillermo want to add a third 6\% solution.  They still have 100 patients and now have 3.5 liters of Precalodine on hand. They want to give the 2\% solution to twice as many patients as the 6\% solution. How many patients should be given each dose?

  \textbf{Hint: }  You'll be dealing with a $3\times 3$ matrix. Use the adjugate and determinant \textbf{calculator} on Google Classroom!

\end{questions}

\end{document}